Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-10-02 trunk/papers/2012-sandwich/CholColloids.tex
Main text to include new figures
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2155 40876441-3496-0410-a613-a2fca35b2ae2

@@

\begin{figure}
\centerline{\includegraphics[width=15.cm]{Fig1.jpg}}
\caption{Snapshots of the steady states obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=5\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supporting Information.] For clarity, only a portion of the simulation box (a quarter of
each axis in size) is shown; the full structures are shown in Fig. S2 and S3.}
\end{figure}

%\begin{figure}
%\includegraphics[width=\textwidth]{s2.jpg}
%\caption{Steady states obtained by dispersing colloids in an isotropic phase and then quenching into the range where BPI is stable, leading to formation of an amorphous disclination network. Parameters otherwise as in Fig.~2.}
%\end{figure}

\begin{figure}
\centerline{\includegraphics[width=15.cm]{Fig2.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig. 1, only a portion of the simulation box is shown for clarity;
the full structures are shown in Fig. S5 and S6.}
\end{figure}

%\begin{figure}
%\includegraphics[width=\textwidth]{s4.jpg}
%\caption{As Fig.~4, but with planar anchoring of the director 
%field at the boundaries.}
%\end{figure}

\begin{figure}
\centerline{\includegraphics[width=15.cm]{Fig3.png}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase, then quenched into a regime where BPIII is stable in the bulk (A), and finally subjected to an electric field along the vertical direction (B). The electric field leads to the formation of a honeycomb structure with hexagonal ordering perpendicular to the field direction. 
Structures correspond to $w=0.23$ and $\phi=1\%$ (see Supporting Information
for full list of parameters). }
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Main text for ``sandwich'' manuscript
%
%  Process with ``pdflatex CholColloids.tex''
%
%  The supporting material text is support.tex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{Snapshots of the states obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=5\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supporting Information.] For clarity, only a portion of the simulation box (a quarter of
each axis in size) is shown; the full structures are shown in Fig. S2 and S3.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig2.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig. 1, only a portion of the simulation box is shown for clarity;
the full structures are shown in Fig. S5 and S6.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig3.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase, then quenched into a regime where BPIII is stable in the bulk (A), and finally subjected to an electric field along the vertical direction (B). The electric field leads to the formation of a honeycomb structure with hexagonal ordering perpendicular to the field direction. 
Structures correspond to $w=0.23$ and $\phi=1\%$ (see Supporting Information
for full list of parameters). }
\end{figure}
